### 2021-04-05 Chapter-4/Chapter-4.tex
Updates from Overleaf

We write simple encryption and decryption function with the above libraries. After that, we build
the source code into 32-bit binary executions. The configuration of our experiment is shown as
\begin{itemize}
\end{itemize}
follows.
\begin{itemize}
\item CPU: 2.90GHz Intel Xeon(R) E5-2690 CPU
\item Memory: 128 GB
\item OS: Ubuntu 18.04 LTS
\item Compiler: GCC 7.5
\end{itemize}

>>>>

We write simple encryption and decryption function with the above libraries. After that, we build
the source code into 32-bit binary executions. The configuration of our experiment is shown as follows.
\begin{itemize}
\item CPU: 2.90GHz Intel Xeon(R) E5-2690 CPU
\item Memory: 128 GB
\item OS: Ubuntu 18.04 LTS
\item Compiler: GCC 7.5
\end{itemize}

Table~\ref{chapter4:table:over_result} shows the overview of evaluation results. 
\tool{} also finds that most side-channel
vulnerabilities leak very little information in practice, which confirms our
initial assumption.  
However, \tool{} finds some vulnerabilities with severe
leakages. Prior research has confirmed that some of these
vulnerabilities can be exploited in real attacks.
With our tool, developers can
distinguish non-critical ``vulnerabilities'' from severe ones.

Symmetric encryption implementations in OpenSSL and mbedTLS have significant leakage due to their lookup table implementations. 
\tool{} confirms that those leakage comes from table lookups. The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem. Those changes are rather easy but significantly decrease the total amount of leaked information as the quantification result indicates.

\tool{} can estimate how
much information is leaked from each vulnerability. During the evaluation,
for each leakage site, \tool{} will stop once 1) it has 95\% confidence
that the error of the estimated leaked information is less than 1 bit,
which gives the leakage quantification a \emph{precision guarantee}, 
or 2) it cannot reach the termination condition after 10 minutes.  In
the latter case, it means \tool{} cannot estimate the amount of leakage with a
probabilistic guarantee. We manually check these leakage sites and find most of them are quite severe.
We will present the details in the subsequent sections.
